---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  warning = FALSE,
  message = FALSE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# pRycollection

<!-- badges: start -->
[![R-CMD-check](https://github.com/schneiderpy/pRycollection/workflows/R-CMD-check/badge.svg)](https://github.com/schneiderpy/pRycollection/actions)
[![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.16744968.svg)](https://doi.org/10.5281/zenodo.16744968)
<!-- badges: end -->

The main goal of **pRycollection** is to provide datasets about Paraguay for
research and teaching that are not easily found or accessible. 
pRycollection is a combination of the 3-letter code for Paraguay - PRY - 
and the word collection. The 3-letter code was chosen to avoid possible
confusion with the programming language Python (py).



## Installation

You can install the development version of pRycollection from [GitHub](https://github.com/) with:

``` {r}
# install.packages("remotes")
remotes::install_github("schneiderpy/pRycollection")
```

## About the data

The pRycollection data package was build from the beginning with FAIR
principles in mind. FAIR stands for **F**indable, **A**ccessible,
**I**nteroperable, and **R**eusable. These principles are critical to
maximizing the impact and value of data in research and practice.

The data is hosted at [Zenodo](https://doi.org/10.5281/zenodo.16744968)

To see what datasets are included in the package load the pRycollection
data package and the dataset package (to access meta data). The type the
following code line:

```{r}
library(pRycollection)
library(dataset) #accessing meta data
data(package = "pRycollection")
```

This will open a new tab in your source pane listing all available datasets.


## Examples

This is a basic example which shows you how to use pRycollection.
Let's use the `py_temperature` dataset.

The first six rows of the dataset ...

```{r example}
head(py_temperature)
```

... the dimensions of the dataset ...

```{r py_temperature}
dim(py_temperature)
```

... or a summary of the dataset.

```{r}
summary(py_temperature)
```
You might have noticed that the dataset has additional and more informative
meta data.


