---
title: "Access meta data"
author: "Andreas Schneider"
description: >
  How to access meta data from the dataset
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Access meta data}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  markdown: 
    wrap: 72
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  warning = FALSE,
  message = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

```

```{r, echo=FALSE}
library(pRycollection)
library(dataset)
```

So far computational results are as expected, as we have seen in
previous [vignettes](https://schneiderpy.github.io/pRycollection/articles/pRycollection.html).

However, we have just seen additional meta data on a glance.
In our `py_temperature` data, what is the unit for the `avg_temp` variable?

To find this out we need the `dataset` package. Since all meta
data has been added with this package we need some functionality of this
package. For more details see the
[documentation](https://dataset.dataobservatory.eu/reference/index.html)
of the package.

Make sure you have installed and load the `dataset` package.

``` r
# load dataset
library(dataset)
```

```{r}
# load data locally
data("py_temperature")
```

The `summary()` function gives a complete overview of the data and meta
data.

```{r}
summary(py_temperature)
```

While this might be a good idea at the beginning, you might be just
interested in the unit of measure of one variable. Just type the one line
of code:

```{r}
var_unit(py_temperature$avg_temp)

```

To see what the data is about, use the `description()` function:

```{r}
description(py_temperature)
```

And for a more complete description:

```{r}
print(get_bibentry(py_temperature), "bibtex")
```

As you can see, the dataset has rich additional meta data along with the actual measured data. Meta data fields are easily accessible which makes guessing unnecessary.
