---
title: "Download all pRycollection datasets"
author: "Andreas Schneider"
description: >
  Download pRycollection datasets from repository
output:
  rmarkdown::html_vignette:
    toc: TRUE
    
vignette: >
  %\VignetteIndexEntry{Download all pRycollection datasets}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

You can get all available datasets at once in a .csv format from the
Zenodo repository.
Make sure you have the [frictionless](https://github.com/frictionlessdata/frictionless-r)
r package installed before proceeding.

```{r setup, warning=FALSE, message=FALSE}
#install.package("frictionless")
library(frictionless)
```


```{r}
# Read data from datapackage.json

pRydata <- frictionless::read_package(
  "https://zenodo.org/records/16744968/files/datapackage.json"
)
pRydata
```

Calling the variable `pRydata` gives you all datasets.
Select the data you are interested in as follow and print the first six
rows of the `py_temperature` data.

```{r}
py_temperature <- read_resource(pRydata, "py_temperature")
head(py_temperature)
```

All datasets have additional metadata, but stored in a separate `json` 
file. If you are interested in the schema type the following two lines
of code:
 
```{r}
temp_schema <- pRydata |>
  get_schema("py_temperature")
str(temp_schema)
```


> If you use the package or any dataset from this package, please cite
the package or dataset.

```{r}
citation("pRycollection")
```


