---
title: "Get started with pRycollection"
author: "Andreas Schneider"
description: >
  Learn how to use pRycollection
output:
  rmarkdown::html_vignette:
    toc: TRUE
  
vignette: >
  %\VignetteIndexEntry{Get started with pRycollection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


> Note that this package is a *work in progress*! New data will be added
as soon as they become available.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  warning = FALSE,
  message = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)

```

```{r setup, include=FALSE, echo=FALSE}
library(pRycollection)
library(dataset)
```

Metadata can provide much more context than they usually do, because
often data and their respective metadata live in separate places. This
can make data analysis more difficult.

The main goal of **pRycollection** is to provide datasets about Paraguay
for research and teaching that are not easily found or accessible.
The data package was build from the beginning with FAIR
principles in mind. FAIR stands for **F**indable, **A**ccessible,
**I**nteroperable, and **R**eusable.
These principles are critical to maximizing the impact and value of
data in research and practice.


> You can download all dataset directly from `vignette("download")`


## Installation

The pRycollection package is easy to install and even more easier to use:

You can install the development version of pRycollection from [GitHub](https://github.com/schneiderpy) with:

```{r, eval=FALSE}
# install.packages("pak")
pak::pak("schneiderpy/pRycollection")
```

## Examples

Choose an available dataset from the package:

```{r, eval=FALSE, warning=FALSE}
# you will see a new pane tab with the available datasets
data(package = "pRycollection")
```

The first six rows of the dataset ...

```{r example}
head(py_temperature)
```

You might have noticed that the dataset has additional variable metadata
labeled with `defined`. Additional metadata was added with the
[dataset](https://dataset.dataobservatory.eu/) package. The new data frames
are stored in an R native format to avoid loss of metadata and to keep
data and metadata together.

For example, if you are interested in the unit of measure for `avg_temp` variable,
type the following line of code:

```{r}
dataset::var_unit(py_temperature$avg_temp)
```

