---
title: "Get started with pRycollection"
author: "Andreas Schneider"
description: >
  Learn how to use pRycollection
output:
  rmarkdown::html_vignette:
    toc: TRUE
  
vignette: >
  %\VignetteIndexEntry{Get started with pRycollection}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---


```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "75%",
  warning = FALSE,
  message = FALSE,
  fig.retina = 2,
  fig.align = 'center'
)
library(pRycollection)
library(frictionless)
library(dataset)
```

Metadata can provide much more context than they usually do, because
often data and their respective metadata live in separate places. This
can make data analysis more difficult.

The main goal of **pRycollection** is to provide datasets about Paraguay
for research and teaching that are not easily found or accessible.
The data package was build from the beginning with FAIR
principles in mind. FAIR stands for **F**indable, **A**ccessible,
**I**nteroperable, and **R**eusable.
These principles are critical to maximizing the impact and value of
data in research and practice.


> You can download all dataset directly from `vignette("download")`


## Installation

You can install the development version of pRycollection from [GitHub](https://github.com/schneiderpy) with:

```r
# install.packages("pak")
pak::pak("schneiderpy/pRycollection")

# load pRycollection
library(pRycollection)
```


## Examples

Choose an available dataset from the package:

```{r}
# you will see a new pane tab with the available datasets
data(package = "pRycollection")
```

Choose your dataset and print the first six rows...

```{r example}
head(py_temperature)
```

You might have noticed that the dataset looks like a normal dataset,
however, with additional meta data. The additional meta data was added
with the [dataset](https://github.com/dataobservatory-eu/dataset/) R package.
For example, you observe the author, year, title, and reference of the 
dataset.

The new data frames are stored in an R native format to avoid loss of
meta data and to keep data and meta data together.

For example, if you are interested in the unit of measure for `avg_temp`
variable, type the following line of code:

```{r}
attributes(py_temperature$avg_temp)

# or alternatively
# attributes(py_temperature[[6]])

```

As you can see the unit of measure is "degrees Celsius".

